Dac summary 01/19/2021

### 2021-11-17 final_dac_summary_pull_20210119.Rmd
making subsets for Tim

This script goes through data that has been returned from the DAC on 1/19 and summarizes it
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```

@@

@@

##########################################################
#                Step 8 - Regressions                    #
##########################################################

@@

@@

>>>>

This script goes through data that has been returned from the DAC on 1/19 and summarizes it
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```

@@

#------ Group for Tim to check quality issues ----------
write.csv(data_empi_acc_f_phq, "/Users/eballer/BBL/msdepression/data/dac/data_empi_acc_f_q.csv", col.names = T, sep = ",")

subset <- subset(data_empi_acc_f_phq, select = c("ACCESSION_NUM","EMPI","EXAM_DATE","depGroupVar"))

melissa_qc_data <- read.csv("/Users/eballer/BBL/msdepression/data/dac/just_empi_date_rating", sep = ",", header = F) #n = 2841
names(melissa_qc_data) <- c("EMPI", "EXAM_DATE", "rating")
subset_with_qc <- merge(subset, melissa_qi_data, by = c("EMPI", "EXAM_DATE"))

write.csv(subset_with_qc, "/Users/eballer/BBL/msdepression/data/dac/subset_with_qc_for_tim_20211117.csv", col.names = T)

@@

##########################################################
#          Step 8 - Visualize all Tracts                 #
##########################################################
just_dep_and_empi <- subset(data_empi_acc_f_phq, select = c("EMPI", "depGroupVar"))
added_dep_to_fascicles <- merge(just_dep_and_empi, fascicle_proportions, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))
lesioned <- subset(melted_df, value > 0)
lesioned_dx <- subset(lesioned, depGroupVar != 0)
healthy <- subset(lesioned, depGroupVar == -1)
depressed <- subset(lesioned, depGroupVar == 1)

q<-ggplot(lesioned, aes(x=value, fill=depGroupVar)) + geom_histogram() + facet_wrap(~variable)
r<-ggplot(lesioned_dx, aes(x=value, fill=depGroupVar)) + geom_histogram() + facet_wrap(~variable)
x<-ggplot(lesioned, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
y<-ggplot(healthy, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
z<-ggplot(depressed, aes(x=value)) + geom_histogram() + facet_wrap(~variable)
print(q)
print(r)
print(x)
print(y)
print(z)

##########################################################
#                Step 9 - Regressions                    #
##########################################################

@@

```{r age_effects_fascicles_unique}
########### age effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,]  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

```{r age_effects_fascicles_mm}
########### age effect whole group

#isolate out only the depressed group and healthy group

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

#lm
fascicle_age_lm <- lapply(fascicle_names, function(x) 
{
  lmerTest::lmer(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names

@@

```{r sex_effects_fascicles_unique}
########### sex effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,]  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

```{r sex_effects_fascicles_mm}
########### sex effect whole group

#lm
fascicle_sex_lm <- lapply(fascicle_names, function(x) 
{
  lmerTest::lmer(substitute(i ~ osex + (1|EMPI), list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names
